A deeper look into bug fixes: patterns, replacements, deletions, and additions

### 2016-02-13 MSRChallenge2016.tex
Into done

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
% 2nd. author
\alignauthor Chu Pan Wong   
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 3rd. author
\alignauthor Ferdinand Lastname
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\section{Introduction}
Automatic bug repair is the branch of computer science that deals with automated ways to repair errors in software. There have been several approaches taken towards improving the different methodologies to repair bugs in software automatically \cite{dongsun}\cite{weimer}\cite{claire} \cite{kai}, one of the most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, which is an evolutionary program repair tool and applies four different kinds of possible changes to code in order to find a patch for a given bug. These changes are the following: Delete, Replace, Swap and Append.

@@

\begin{table*}
\centering
\caption{Amount of appearances per replace kind}
\resizebox{\textwidth}{100pt}{
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
 &Assert&Break&Continue&Do& For&If&Label&Return&Switch&Switch& Synchronized&Throw&Try&TypeDecl&While
\\ \hline
\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
\\ \hline
\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
 \\ \hline
\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
 \\   \hline
\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
  \\ \hline
\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
 \\ \hline
\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
 \\ \hline
\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
\\ \hline
\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
 \\ \hline
\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
\\ \hline
\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
 \\ \hline
\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
 \\ \hline
\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
 \\ \hline
\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
 \\ \hline
\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
 \\ \hline
\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
 \\ \hline
\end{tabular}
}
\end{table*}

>>>>

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{email@domain.com}
% 2nd. author
\alignauthor Chu Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{clegoues@cs.cmu.edu}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\section{Introduction}
Automatic bug repair is the branch of computer science that deals with automated ways to repair errors in software. There have been several approaches taken towards improving the different methodologies to repair bugs in software automatically \cite{dongsun}\cite{weimer}\cite{claire} \cite{kai}, one of the most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an evolutionary program repair tool which applies four different kinds of possible edits to code in order to find a patch for a given bug. These changes are the following: Delete, Replace, Swap and Append.

Another well known approach is PAR \cite{dongsun}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair it. In this paper we have taken 7 out of the 10 PAR templates and tested how common they are in the repairs made by programmers in the latest official data dump of Github as of September 2015 provided by \cite{robert}.

@@

\begin{table*}
\centering
\caption{Amount of appearances per replace kind}
\resizebox{\textwidth}{100pt}{
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
 &Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
\\ \hline
\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
\\ \hline
\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
 \\ \hline
\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
 \\   \hline
\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
  \\ \hline
\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
 \\ \hline
\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
 \\ \hline
\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
\\ \hline
\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
 \\ \hline
\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
\\ \hline
\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
 \\ \hline
\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
 \\ \hline
\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
 \\ \hline
\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
 \\ \hline
\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
 \\ \hline
\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
 \\ \hline
\end{tabular}
}
\end{table*}
